Experimental Analysis of a Spatialised Audio Interface for People with Visual Impairments

### 2020-05-12 paper.tex
Updated stats, figures. Modified discussion

A post-hoc analysis using the Wilcoxon signed rank test, with a Holm-Bonferroni correction applied to the commonly used 0.05 threshold, was used to investigate the setting relationships more closely. 
This analysis reveals that there is a significant difference between the errors generated by the \textit{lo} and \textit{med} settings, as well as the \textit{lo} and \textit{hi} settings, for Group~\textit{G1} ($p_{lo-med} = 0.003,~p_{lo-hi} < 0.001$), showing that the \textit{lo} setting clearly produces the highest error, while it is not clear which one of the \textit{med} and \textit{hi} settings is better for Group~\textit{G1}. 
Based on the current data, it is impossible to conclude which setting produces the smallest angular error for Group~\textit{G2}, but this may because of the relatively small sample size for each setting. 
\hlbreakable{Furthermore, the significant variance in the error results for Group \textit{G2} could possibly be because of the higher mean age compared to Group \textit{G1} and their general inexperience with mobile phones.
However, comparing the distributions for each setting between the two groups with the Kruskal-Wallis test for non-parametric data, we see that the differences between the distributions for all three settings are not significantly different, for both groups and both pan and elevation (the $p$-values are summarised in \cref{tab:inter-group-results}).}
The similarity between the differences is further highlighted with non-significant results from the two-sided Kolmogorov-Smirnov test ($p > 0.05$ for both groups and all three test conditions).\todo{include these p-values in the table?}
\hlbreakable{This result confirms that the performance of the blindfolded participants and those with severe sight impairments are statistically similar despite the seemingly clear differences in error performance.
Therefore, groups from a different population can reasonably be expected to produce similar errors under similar experimental conditions. 
We also note that there is a significant negative error bias in the elevation data for all the settings and groups, possibly caused by a cognitive constraint introduced by the floor, below which the participants believed the targets could not appear.
Since this bias seems to be constant, it could be easily addressed in a future version of the audio interface by adjusting its frequency parameters to shift the bias upwards by a constant offset. 
Finally, we can conclude that the \textit{hi} setting, which generates the significantly smallest elevation error, is the best audio pitch level to guide a user in a pointing task, and that the pan error is completely independent of such setting choice. }

\begin{table}
  \centering
  \caption{A summary of the $p$-values from the Kruskal-Wallis test comparing the distributions of the different settings' error data for each group in both the pan and elevation dimensions. }\label{tab:inter-group-results}
  \begin{tabular}{lll}
    \toprule
                   & Pan      & Elevation \\ \midrule
      \textit{lo}  & $p=0.18$ & $p=0.90$  \\
      \textit{med} & $p=0.86$ & $p=0.34$  \\
      \textit{hi}  & $p=0.28$ & $p=0.38$  \\
    \bottomrule
  \end{tabular}
\end{table}

@@

These results allows us to calculate and plot in \cref{fig:fitts-ips} an index of performance, as given by \cref{eq:fitts-performance}, for each audio setting.
The results are summarised in \cref{tab:fitts-results}.
For Group~\textit{G1}, there is a fairly consistent level of performance between the three settings, with \textit{lo} producing the highest indices of performance overall (i.e.\ the participants found the targets with the smallest error and in the least amount of time).
\hlbreakable{This is supported by the results from the Friedman test, showing that there is a significant difference in performance between the settings ($p < 0.001$), as well as post-hoc Wilcoxon tests with Holm-Bonferroni corrections, which show that the \textit{lo} setting is significantly different to the \textit{med} and \textit{hi} settings ($p_{lo-med} < 0.001,~p_{lo-hi} < 0.001$). 
The \textit{med} and \textit{hi}, instead, are not significantly different from each other ($p_{med-hi} = 0.85$).}
The results for Group~\textit{G2} show generally lower and inconsistent indices of performance for each setting, which is expected given the increased times to target observed in \cref{fig:fitts-results}.
Again, from the Friedman test ($p < 0.001$), the \textit{lo} setting produces the highest performance by a large margin, compared to the \textit{med} setting, with the Wilcoxon test and Holm-Bonferronni corrections ($p_{lo-med}=0.01$), followed by the \textit{hi} and \textit{med} settings' results, respectively.
This seems to indicate that, for both groups, the \textit{lo} setting produces the highest level of performance, followed by the \textit{hi} setting.

\begin{table}
  \centering
  \caption{The average target acquisition error in the pan and elevation dimensions for each participant group. }\label{tab:fitts-results}
  \begin{tabular}{p{0.5cm}p{1.5cm}p{2.5cm}}
    \toprule
    & Setting      & Mean Index of Performance \\ \midrule
    & \textit{lo}  & $0.056\pm0.005$ \\
    \textit{G1} & \textit{med} & $0.053\pm0.008$ \\
		& \textit{hi}  & $0.051\pm0.007$ \\ \cline{2-3}
    & \textit{lo}  & $0.034\pm0.009$ \\
    \textit{G2} & \textit{med} & $0.014\pm0.002$ \\
    & \textit{hi}  & $0.022\pm0.006$ \\
    \bottomrule
  \end{tabular}
\end{table}

\cref{fig:fitts-ips} shows a significant difference between the IPs for each group's respective settings, with \textit{G2} producing significantly lower indices of performance.
This is further supported by the Kruskal-Wallis test, revealing that each setting's distribution is indeed significantly different from its counterpart in the other group ($p_{lo} < 0.001,~p_{med} < 0.001,~p_{hi} < 0.001$).
The significant difference between the blindfolded group and the group of participants with visual impairments seems to indicate that the latter require significantly more time to find the target. 
However, it is unclear whether this is a systematic cause or a difference in search strategy between the two groups, e.g.\ \textit{G2} preferring, on average, a slower and more methodical approach.

@@

The results for the accuracy and time performance with the proposed audio interface shows an interesting contrast.
That is, the \textit{hi} pitch setting produces the lowest target acquisition error, followed by the \textit{med} and \textit{lo} settings, respectively. 
However, this trend is almost wholly reversed in the time-to-target results from the Fitts model, where the \textit{lo} setting gives the highest level of performance, followed by the \textit{hi} and \textit{med} settings respectively. 
Since Fitts's model takes the angular error into account, one might reasonably expect that the results for both experiments follow a similar trend. 
However, the Fitts model does not account for changing stimuli and different strategies.
We therefore hypothesise that the reason for this divergence in performance is due to the increased resolution of the \textit{hi} setting, which allows for finer adjustments of the device's orientation, getting it closer to the correct target, but at the cost of a higher average time-to-target. 
This seems to indicate a speed/accuracy trade-off in finding the targets.
With the Fitts model discussed here, we can modify the interface to prioritise different metrics and produce the correct output.

>>>>

A post-hoc analysis using the Wilcoxon signed rank test, with a Holm-Bonferroni correction applied to the commonly used 0.05 threshold, was used to investigate the setting relationships more closely. 
This analysis reveals that there is a significant difference between the errors generated by the \textit{lo} and \textit{med} settings, as well as the \textit{lo} and \textit{hi} settings, for Group~\textit{G1} ($p_{lo-med} = 0.003,~p_{lo-hi} < 0.001$), showing that the \textit{lo} setting clearly produces the highest error, while it is not clear which one of the \textit{med} and \textit{hi} settings is better for Group~\textit{G1}. 
Based on the current data, it is impossible to conclude which setting produces the smallest angular error for Group~\textit{G2}, but this may because of the relatively small sample size for each setting. 
\hlbreakable{Furthermore, the significant variance in the error results for Group \textit{G2} could possibly be because of the higher mean age compared to Group \textit{G1} and their general inexperience with mobile phones.
Indeed, previous works have suggested that these demographics may have a measurable effect on target-finding performance~\citep{millar1994understanding,pring2008psychological}.
However, comparing the distributions for each setting between the two groups with the Kruskal-Wallis test for non-parametric data, we see that the differences between the distributions for all three settings are not significantly different, for both groups and both pan and elevation (the $p$-values are summarised in \cref{tab:inter-group-results}).}
The similarity between the differences is further highlighted with non-significant results from the two-sided Kolmogorov-Smirnov test, where none of the $p$-values are significant.
The $p$-values for this test are also listed in~\cref{tab:inter-group-results}.
\hlbreakable{This result confirms that the performance of the blindfolded participants and those with severe sight impairments are statistically similar despite the seemingly clear differences in error performance.
Therefore, groups from a different population can reasonably be expected to produce similar errors under similar experimental conditions. 
We also note that there is a significant negative error bias in the elevation data for all the settings and groups, possibly caused by a cognitive constraint introduced by the floor, below which the participants believed the targets could not appear.
Since this bias seems to be constant, it could be easily addressed in a future version of the audio interface by adjusting its frequency parameters to shift the bias upwards by a constant offset. 
Finally, we can conclude that the \textit{hi} setting, which generates the significantly smallest elevation error, is the best audio pitch level to guide a user in a pointing task, and that the pan error is completely independent of such setting choice. }

\begin{table}
  \centering
  \caption{A summary of the $p$-values from the Kruskal-Wallis and Kolmogorov-Smirnov tests comparing the distributions of the different settings' error data for each group in both the pan and elevation dimensions. }\label{tab:inter-group-results}
  \begin{tabular}{lcccc}
    \toprule
		   & \multicolumn{2}{c}{Kruskal-Wallis} & \multicolumn{2}{c}{Kolmogorov-Smirnov} \\
		   & Pan      & Elevation & Pan      & Elevation \\ \midrule
      \textit{lo}  & $p=0.18$ & $p=0.90$  & $p=0.07$ & $p=0.91$  \\
      \textit{med} & $p=0.86$ & $p=0.34$  & $p=0.90$ & $p=0.36$  \\
      \textit{hi}  & $p=0.28$ & $p=0.38$  & $p=0.61$ & $p=0.31$  \\
    \bottomrule
  \end{tabular}
\end{table}

@@

These results allows us to calculate and plot in \cref{fig:fitts-ips} an index of performance, as given by \cref{eq:fitts-performance}, for each audio setting.
The results are summarised in \cref{tab:fitts-results}.
For Group~\textit{G1}, there is a fairly consistent level of performance between the three settings, with \textit{med} producing the highest indices of performance overall (i.e.\ the participants found the targets with the smallest error and in the least amount of time).
\hlbreakable{This is supported by the results from the Friedman test, showing that there is a significant difference in performance between the settings ($p < 0.001$), as well as post-hoc Wilcoxon tests with Holm-Bonferroni corrections, which show that the \textit{med} setting is significantly different to the \textit{lo} and \textit{hi} settings ($p_{med-lo} < 0.001,~p_{med-hi} < 0.001$). 
The \textit{lo} and \textit{hi} settings, instead, are not significantly different from each other ($p_{lo-hi} = 0.11$).
The results for Group~\textit{G2} show generally lower indices of performance for each setting, which is expected given the increased times to target observed in \cref{fig:fitts-results}.
%However, the \emph{hi} setting's result is an exception here and has a far smaller gap between it and its counterpart in Group \emph{G1}.
Following visual inspection of the distribution and significant results from the Friedman test ($p < 0.001$), it is clear that the \textit{hi} setting produces the highest performance by a large margin, compared to the \textit{lo} and \textit{med} settings. 
This is supported by Wilcoxon tests ($p_{lo-hi}=0.01$, $p_{med-hi}=0.01$), which also show that the results for the \textit{lo} and \textit{med} settings are not different ($p_{lo-med}=0.09$).}

%This seems to indicate that, for both groups, the \textit{lo} setting produces the highest level of performance, followed by the \textit{hi} setting.

\begin{table}
  \centering
  \caption{The average target acquisition error in the pan and elevation dimensions for each participant group. }\label{tab:fitts-results}
  \begin{tabular}{p{0.5cm}p{1.5cm}p{2.5cm}}
    \toprule
                & Setting      & Mean Index of Performance \\ \midrule
                & \textit{lo}  & $0.054\pm0.005$ \\
    \textit{G1} & \textit{med} & $0.057\pm0.006$ \\
		& \textit{hi}  & $0.054\pm0.007$ \\ \cline{2-3}
                & \textit{lo}  & $0.039\pm0.007$ \\
    \textit{G2} & \textit{med} & $0.038\pm0.007$ \\
                & \textit{hi}  & $0.048\pm0.008$ \\
    \bottomrule
  \end{tabular}
\end{table}

\cref{fig:fitts-ips} shows a significant difference between the IPs for each group's respective settings, with \textit{G2} producing significantly lower indices of performance.
This is further supported by a Kruskal-Wallis tests that reveals that each setting's distribution is indeed significantly different from its counterpart in the other group.
The significant difference between the blindfolded group and the group of participants with visual impairments seems to indicate that the latter require significantly more time to find the target. 
However, it is unclear whether this is a systematic cause or a difference in search strategy between the two groups, e.g.\ \textit{G2} preferring, on average, a slower and more methodical approach.

@@

\begin{highlighted}
Since Fitts's model we used here is based on the target estimation errors, it is reasonable to expect that the accuracy and time performances will follow similar trends. 
Indeed, this seems to be the case, with the \textit{hi} pitch setting produces the lowest target acquisition error, followed by the \textit{med} and \textit{lo} settings, respectively. 
This trend continues in the time-to-target results obtained with the Fitts model analysis, where the \textit{med} setting gave the marginally highest level of performance in Group \textit{G1} and \textit{hi} for Group \textit{G2}.
However, the improvement of the latter settings are far clearer in Group \textit{G2} than for \textit{G1}.
Indeed, Group \textit{G2} seems to respond better to the increased movement resolution that the \textit{hi} affords the use, allowing for finer adjustments to be made to the device's orientation to get closer to the target.
With the Fitts model discussed here, we can empirically evaluate any changes we make to the audio interface and optimise the parameters it to produce the desired output. 
\end{highlighted}
%However, this trend is almost wholly reversed in the time-to-target results from the Fitts model, where the \textit{lo} setting gives the highest level of performance, followed by the \textit{hi} and \textit{med} settings respectively. 
%Since Fitts's model takes the angular error into account, one might reasonably expect that the results for both experiments follow a similar trend. 
%However, the Fitts model does not account for changing stimuli and different strategies.
%We therefore hypothesise that the reason for this divergence in performance is due to the increased resolution of the \textit{hi} setting, which allows for finer adjustments of the device's orientation, getting it closer to the correct target, but at the cost of a higher average time-to-target. 
%This seems to indicate a speed/accuracy trade-off in finding the targets.
%With the Fitts model discussed here, we can modify the interface to prioritise different metrics and produce the correct output.
